\begin{thebibliography}{99}

% 1. Networking and Protocols
\bibitem{rfc6455}
Fette, I., \& Melnikov, A. (2011).
\textit{The WebSocket Protocol}. RFC 6455, IETF.\\
\url{https://datatracker.ietf.org/doc/html/rfc6455}

\bibitem{fielding2000}
Fielding, R. T. (2000).
\textit{Architectural Styles and the Design of Network-based Software Architectures} (Doctoral dissertation). University of California, Irvine.

% 2. Apple Documentation
\bibitem{apple2023}
Apple Inc. (2023).
\textit{URLSession – Foundation | Apple Developer Documentation}.\\
\url{https://developer.apple.com/documentation/foundation/urlsession}

\bibitem{websocketswift}
Apple Inc. (2023).
\textit{URLSessionWebSocketTask – Foundation | Apple Developer Documentation}.\\
\url{https://developer.apple.com/documentation/foundation/urlsessionwebsockettask}

\bibitem{metalguide}
Apple Inc. (2023).
\textit{Metal Programming Guide}.\\
\url{https://developer.apple.com/metal/}

% 3. NLP and Machine Learning
\bibitem{jurafsky2019}
Jurafsky, D., \& Martin, J. H. (2019).
\textit{Speech and Language Processing} (3rd ed. draft). Stanford University.\\
\url{https://web.stanford.edu/~jurafsky/slp3/}

\bibitem{paszke2017}
Paszke, A., et al. (2017).
\textit{Automatic Differentiation in PyTorch}. NIPS 2017.\\
\url{https://openreview.net/pdf?id=BJJsrmfCZ}

\bibitem{goldberg2017}
Goldberg, Y. (2017).
\textit{Neural Network Methods for Natural Language Processing}. Morgan \& Claypool.

\bibitem{grinberg2018}
Grinberg, M. (2018).
\textit{Flask Web Development} (2nd ed.). O'Reilly Media.

% 4. LSTM-related Research
\bibitem{hochreiter1996}
Hochreiter, S., \& Schmidhuber, J. (1996).
\textit{LSTM Can Solve Hard Long Time Lag Problems}. NIPS 1996.\\
\url{https://www.researchgate.net/publication/221620298}

\bibitem{hochreiter1997}
Hochreiter, S., \& Schmidhuber, J. (1997).
\textit{Long Short-Term Memory}. Neural Computation, 9(8), 1735–1780.\\
\url{https://doi.org/10.1162/neco.1997.9.8.1735}

\bibitem{arras2019}
Arras, L., et al. (2019).
\textit{Explaining and Interpreting LSTMs}. In Explainable AI, Springer, pp. 211–238.\\
\url{https://arxiv.org/abs/1909.12114}

\bibitem{hoedt2021}
Hoedt, P.-J., et al. (2021).
\textit{MC-LSTM: Mass-Conserving LSTM}. arXiv preprint.\\
\url{https://arxiv.org/abs/2101.05186}

\end{thebibliography}


